Commutative character sheaves and geometric types for supercuspidal representations

### 2017-08-30 CJM/second letter to CJM.tex
Writing letter to editor

\usepackage{amssymb}
\usepackage{amsrefs}
% Fonts
\usepackage{mathrsfs}
% Enumitem
\usepackage{enumitem}
% Hyperrefs
\usepackage{hyperref}
\hypersetup{
  colorlinks   = true, %Colours links instead of ugly boxes
  urlcolor     = blue, %Colour for external hyperlinks
  linkcolor    = blue, %Colour of internal links
  citecolor   = green %Colour of citations
}
\usepackage[margin=3.5cm]{geometry}
%\renewcommand{\baselinestretch}{1.0}

\usepackage{tikz}
\usetikzlibrary{shapes,arrows,calc,matrix}
\usepackage{tikz-cd}
\usepackage{todonotes}

%%%%% for spacing
\usepackage{amsmath}
\usepackage{lipsum}
\usepackage{setspace}

@@

      \newtheorem{conjecture}[theorem]{Conjecture}
%%%%%%%%%%%%%%% RINGS AND GROUPS %%%%%%%%%%%%%%%
\newcommand{\FF}{{\mathbb{F}}}
\newcommand{\ZZ}{{\mathbb{Z}}}
\newcommand{\NN}{{\mathbb{N}}}
\newcommand{\CC}{{\mathbb{C}}}
\newcommand{\QQ}{{\mathbb{Q}}}
\newcommand{\RR}{{\mathbb{R}}}
\newcommand{\EE}{\mathbb{\bar Q}_\ell}
\newcommand{\OK}{\mathcal{O}_K}
\newcommand{\OL}{\mathcal{O}_L}
\newcommand{\OO}[1]{\mathcal{O}_{#1}}
\newcommand{\bFq}{\bar{k}}
\newcommand{\Fq}{k}
\newcommand{\Fqm}{k_m}
\newcommand{\EEx}{\EE^\times}
\newcommand{\ZEx}{\mathbb{\bar Z}_\ell^\times}
\newcommand{\Weil}[1]{\mathcal{W}_{#1}}
\newcommand{\m}{{\mathfrak{m}}}
%%%%%%%%%%%%%%% ALGEBRAIC GROUPS %%%%%%%%%%%%%%%
\newcommand{\Gm}[1]{\mathbb{G}_{\hskip-1pt\textbf{m},#1}}
\DeclareMathOperator{\GL}{GL}
\newcommand{\comp}{\Pi} % Component group
\newcommand{\G}{\textbf{G}}
%%%%%%%%%%%%%%% NAMED OPERATORS %%%%%%%%%%%%%%%
\DeclareMathOperator{\Gal}{Gal}
\newcommand{\Frob}[1]{\operatorname{Fr}_{#1}}
\DeclareMathOperator{\Aut}{Aut}
\DeclareMathOperator{\Hom}{Hom}
\DeclareMathOperator{\ord}{ord}
\DeclareMathOperator{\coker}{coker}
\DeclareMathOperator{\Gr}{Gr}
\DeclareMathOperator{\Irrep}{Irrep}
\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\Ext}{Ext}
\DeclareMathOperator{\Hh}{H}
\DeclareMathOperator{\Res}{Res}
\DeclareMathOperator{\Nm}{Nm}
\DeclareMathOperator{\trace}{Tr}
\DeclareMathOperator{\obj}{obj}
\DeclareMathOperator{\mor}{mor}
\DeclareMathOperator{\Lang}{Lang}
\DeclareMathOperator{\image}{im}
\DeclareMathOperator{\Loc}{Loc}
\DeclareMathOperator{\Tot}{Tot}
\DeclareMathOperator{\Tor}{Tor}
\DeclareMathOperator{\SL}{SL}
\DeclareMathOperator{\PGL}{PGL}
\newcommand{\gal}[1]{{\operatorname{Gal}\hskip-1pt\left( {\bar #1}/#1 \right)}}
\newcommand{\Spec}[1]{{\operatorname{Spec}(#1)}}
\newcommand{\op}{_{\operatorname{op}}}
\newcommand{\der}{_{\operatorname{der}}}
\newcommand{\ab}{_{\operatorname{ab}}}

@@

\setcounter{equation}{-1}

@@

@@

\begin{enumerate}
\item[(1)]
\end{enumerate}

\begin{enumerate}
\item[(i)] Thank you for noticing this. We referred to the geometric type $\cs{F}^d$ constructed in the paper as a virtual sheaf complex, but this is misleading, since that would reasonably be interpreted as an element in the Grothendieck group of sheaf complexes, while the geometric type is an element of the group obtained by tensoring this Grothendieck group with  $\QQ$. To clarify this, we have used the term {\it rational virtual} for formal linear combinations of sheaf complexes, with rational coefficients.

\end{enumerate}

>>>>

\usepackage{amssymb}
%\usepackage{amsrefs}
% Fonts
%\usepackage{mathrsfs}
% Enumitem
\usepackage{enumitem}
% Hyperrefs
\usepackage{hyperref}
%\hypersetup{
%  colorlinks   = true, %Colours links instead of ugly boxes
%  urlcolor     = blue, %Colour for external hyperlinks
%  linkcolor    = blue, %Colour of internal links
%  citecolor   = green %Colour of citations
%}
\usepackage[margin=3.5cm]{geometry}
%\renewcommand{\baselinestretch}{1.0}

%\usepackage{tikz}
%\usetikzlibrary{shapes,arrows,calc,matrix}
%\usepackage{tikz-cd}
%\usepackage{todonotes}

%%%%% for spacing
\usepackage{amsmath}
%\usepackage{lipsum}
%\usepackage{setspace}

@@

      \newtheorem{conjecture}[theorem]{Conjecture}
%%%%%%%%%%%%%%% RINGS AND GROUPS %%%%%%%%%%%%%%%
\newcommand{\FF}{{\mathbb{F}}}
\newcommand{\ZZ}{{\mathbb{Z}}}
\newcommand{\NN}{{\mathbb{N}}}
\newcommand{\CC}{{\mathbb{C}}}
\newcommand{\QQ}{{\mathbb{Q}}}
\newcommand{\RR}{{\mathbb{R}}}
\newcommand{\EE}{\mathbb{\bar Q}_\ell}
\newcommand{\OK}{\mathcal{O}_K}
\newcommand{\OL}{\mathcal{O}_L}
\newcommand{\OO}[1]{\mathcal{O}_{#1}}
\newcommand{\bFq}{\bar{k}}
\newcommand{\Fq}{k}
\newcommand{\FFF}{\mathbb{F}_3}
\newcommand{\Fqm}{k_m}
\newcommand{\EEx}{\EE^\times}
\newcommand{\ZEx}{\mathbb{\bar Z}_\ell^\times}
\newcommand{\Weil}[1]{\mathcal{W}_{#1}}
\newcommand{\m}{{\mathfrak{m}}}
%%%%%%%%%%%%%%% ALGEBRAIC GROUPS %%%%%%%%%%%%%%%
\newcommand{\Gm}[1]{\mathbb{G}_{\hskip-1pt\textbf{m},#1}}
\DeclareMathOperator{\GL}{GL}
\newcommand{\comp}{\Pi} % Component group
\newcommand{\G}{\textbf{G}}
%%%%%%%%%%%%%%% NAMED OPERATORS %%%%%%%%%%%%%%%
\DeclareMathOperator{\Gal}{Gal}
\newcommand{\Frob}[1]{\operatorname{Fr}_{#1}}
\DeclareMathOperator{\Aut}{Aut}
\DeclareMathOperator{\Hom}{Hom}
\DeclareMathOperator{\ord}{ord}
\DeclareMathOperator{\coker}{coker}
\DeclareMathOperator{\Gr}{Gr}
\DeclareMathOperator{\Irrep}{Irrep}
\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\Ext}{Ext}
\DeclareMathOperator{\Hh}{H}
\DeclareMathOperator{\Res}{Res}
\DeclareMathOperator{\Nm}{Nm}
\DeclareMathOperator{\trace}{Tr}
\DeclareMathOperator{\obj}{obj}
\DeclareMathOperator{\mor}{mor}
\DeclareMathOperator{\Lang}{Lang}
\DeclareMathOperator{\image}{im}
\DeclareMathOperator{\Loc}{Loc}
\DeclareMathOperator{\Tot}{Tot}
\DeclareMathOperator{\Tor}{Tor}
\DeclareMathOperator{\SL}{SL}
\DeclareMathOperator{\PGL}{PGL}
\newcommand{\gal}[1]{{\operatorname{Gal}\hskip-1pt\left( {\bar #1}/#1 \right)}}
\newcommand{\Spec}[1]{{\operatorname{Spec}(#1)}}
\newcommand{\op}{_{\operatorname{op}}}
\newcommand{\der}{_{\operatorname{der}}}
\newcommand{\ab}{_{\operatorname{ab}}}

@@

%\setcounter{equation}{-1}

@@

In addition to making changes prompted by the referee's comments, we have corrected an error pointed out to us in an e-mail from Will Savin.  Namely, we assumed incorrectly at the beginning of section 3 that any character on $G(k)$ would vanish on $G\der(k)$.  Every character vanishes on $G(k)\der$, but in general these two groups are not the same (for example, if $G = \SL_2$ over $\FFF$ or $\PGL_2$ over a finite field of odd characteristic).  We adjusted the exposition in the introduction and beginning of section 3 to correct this mistake, and added hypotheses in the statements of Corollary 3.8, Thereom 3.12 and Theorem 5.2.  We also added Section 4, where we describe some approaches for geometrizing characters that do not vanish on $G\der(k)$.

We now describe the changes made to address the referee's remarks.

\begin{enumerate}[label=(\arabic*)]
\item We have added Section 3.2.3 on Rigidification to address this problem, and restructured the discussion around what was Lemma 3.3.
\item The new section also addresses this concern.  Note that the reviewer is correct that $n^*_2(\mu)$ agrees with $p^*_2(\mu)$, though we did not add this fact explicitly to the paper, because it was not needed in the discussion of rigidification.
\end{enumerate}

\begin{enumerate}[label=(\roman*)]
\item We have fixed the typo.
\item The reviewer is correct that we do not need smoothness.
\item We have changed all the $i$s to $j$s.
\item We have changed $\cs{L}$ to $(\cs{L}, \mu)$ as suggested.
\item We have added the adjective ``linear'' at various points throughout the paper, including this one.
\item We have added a note as suggested.
\item We couldn't find a way to clarify this without adding a lot of extra material, which we thought would actually hurt the clarify of the exposition.  We therefore left these statements unchanged.
\end{enumerate}

@@
